%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Scientist} % Job title
    {Physical Analysis and Cryptographic Engineering Lab.} % Organization
    {Singapore} % Location
    {Oct. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Deployed modern cryptographic algorithms on hardware (FPGAs)}
        \item {Evaluated the security of cryptographic algorithms against side-channel attack}
        \item {Developed advanced side-channel attacks based on machine-learning}
        \item {Developed secure designs to resist side-channel attacks in hardware and software}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Postdoc.} % Job title
    {University of Twente} % Organization
    {Enschede, The Netherlands} % Location
    {Jan. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a mathematical model to correlate fault-tolerance and heat-generation in 45nm processors}
        \item {Delivered lectures for graduate and undergraduate courses in computer science in CAES group}
	\item {Supervised one PhD student towards finishing his doctorate thesis}
	\item {Leader of a team of four graduate students to finish their final project of SoC design}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {PhD candidate} % Job title
    {University of Twente} % Organization
    {Enschede, The Netherlands} % Location
    {Jun. 2010 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	\item {Developed a software tool to automate reliability assessment of digital circuits}
        \item {Developed a design to increase resilience of DSP processors against radiation-induced faults}
	\item{Published more than 10 technical articles in international journals and conferences, to see the complete list, see the appendices}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {IroC Technologies} % Organization
    {Grenoble, France} % Location
    {Feb. 2012, May. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted evaluation test to evaluate the sensitivity of network card against single-bit faults}
        \item {Developed a reliability evaluation platform to automate fault injection \&  evaluation on hardware}
	\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Recore Systems} % Organization
    {Enschede, The Netherlands} % Location
    {Jan. 2011, May. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the design file of a modern DSP processor used in space applications.}
        \item {Developed a reliable design for the DSP processor which was used by European Space Agency}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
